The connection between star formation rate and dark matter halo mass during reionization

### 2015-09-01 paper/ms.tex
SFR-DMHM graphs. (comparisson with Gonzalez-Perez et. al. and Behroozi et. al.)

@@

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD1_CosmicVar2_w_dust.pdf}
\caption{Best fit parameter distribution due cosmic variance with Willott data in the dust
 attenuation model.}
\label{fig:OD1_CosmicVar2_w_dust}
\end{figure}

@@

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD2_CosmicVar1_wo_dust.pdf}
\caption{Best fit parameter distribution due cosmic variance with Bouwens data in the no-dust
 attenuation model.}
\label{fig:OD2_CosmicVar1_wo_dust}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD3_CosmicVar1_w_dust.pdf}
\caption{Best fit parameter distribution due cosmic variance with McLure data in the dust
 attenuation model.}
\label{fig:OD3_CosmicVar1_w_dust}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD3_CosmicVar1_wo_dust.pdf}
\caption{Best fit parameter distribution due cosmic variance with McLure data in the no-dust
 attenuation model.}
\label{fig:OD3_CosmicVar1_wo_dust}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD4_CosmicVar1_w_dust.pdf}
\caption{Best fit parameter distribution due cosmic variance with Finkelstein data in the dust
 attenuation model.}
\label{fig:OD4_CosmicVar1_w_dust}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD4_CosmicVar1_wo_dust.pdf}
\caption{Best fit parameter distribution due cosmic variance with Finkelstein data in the no-dust
 attenuation model.}
\label{fig:OD4_CosmicVar1_wo_dust}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD1_CosmicVar2_wo_dust.pdf}
\caption{Best fit parameter distribution due cosmic variance with Willott data in the no-dust
 attenuation model.}
\label{fig:OD1_CosmicVar2_wo_dust}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD1_SFR_DMHM_wo.pdf}
\caption{Star formation rate as function of the dark matter halo mass without dust attenuation. 
Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region. 
Comparison with %the GALFORM semi-analitical model \citep{Gonzalez14} and a
an implementation
of abundance matching model \citep{Behroozi13}. }
\label{fig:SFR_DMHM_wo}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD1_SFR_DMHM_w.pdf}
\caption{Star formation rate as function of the dark matter halo mass with dust attenuation. 
Solid lines represents the mean SFR value over the small boxes within $50\%$  shaded region.
Comparison with %the GALFORM semi-analitical model \citep{Gonzalez14} and a
an implementation
of abundance matching model \citep{Behroozi13}. }
\label{fig:_SFR_DMHM_w}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\epsscale{1.00}
\plotone{fig/smallcells/OD2_w_dust_box_1.png} % pdf available
\caption{Parameter dispersion fitting the Bouwens with the Dust Attenuation model. 
$1\sigma$ is defined by the likelihood ratio between 0.0 (red) and 0.5 (green)}
\label{fig:OD2_MCMC_best_steps_w}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/smallcells/OD2_wo_dust_box_1.png} % pdf available
\caption{Parameter dispersion fitting the Bouwens with the No-Dust Attenuation model. 
$1\sigma$ is defined by the likelihood ratio between 0.0 (red) and 0.5 (green)}
\label{fig:OD2_MCMC_best_steps_wo}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\epsscale{1.00}
\plotone{fig/smallcells/OD3_w_dust_box_1.png} % pdf available
\caption{Parameter dispersion fitting the McLure with the Dust Attenuation model. 
$1\sigma$ is defined by the likelihood ratio between 0.0 (red) and 0.5 (green)}
\label{fig:OD3_MCMC_best_steps_w}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/smallcells/OD3_wo_dust_box_1.png} % pdf available
\caption{Parameter dispersion fitting the McLure with the No-Dust Attenuation model. 
$1\sigma$ is defined by the likelihood ratio between 0.0 (red) and 0.5 (green)}
\label{fig:OD3_MCMC_best_steps_wo}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\epsscale{1.00}
\plotone{fig/smallcells/OD4_w_dust_box_1.png} % pdf available
\caption{Parameter dispersion fitting the Finkelstein with the Dust Attenuation model. 
$1\sigma$ is defined by the likelihood ratio between 0.0 (red) and 0.5 (green)}
\label{fig:OD4_MCMC_best_steps_w}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/smallcells/OD4_wo_dust_box_1.png} % pdf available
\caption{Parameter dispersion fitting the Finkelstein with the No-Dust Attenuation model. 
$1\sigma$ is defined by the likelihood ratio between 0.0 (red) and 0.5 (green)}
\label{fig:OD4_MCMC_best_steps_wo}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%\begin{figure}
%\epsscale{1.00}
%\plotone{fig/OD1_CosmicVar2_w_dust.pdf}
%\caption{Best fit parameter distribution due cosmic variance with Willott data in the dust
% attenuation model.}
%\label{fig:OD1_CosmicVar2_w_dust}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}
\epsscale{1.00}
\plotone{fig/smallcells/OD2_plotcosmicvariance_wo_dust.pdf}
\caption{Best fit parameter distribution due cosmic variance with Bouwens data in the no-dust
 attenuation model.}
\label{fig:OD2_CosmicVar1_wo_dust}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}
\epsscale{1.00}
\plotone{fig/smallcells/OD3_plotcosmicvariance_w_dust.pdf}
\caption{Best fit parameter distribution due cosmic variance with McLure data in the dust
 attenuation model.}
\label{fig:OD3_CosmicVar1_w_dust}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/smallcells/OD3_plotcosmicvariance_wo_dust.pdf}
\caption{Best fit parameter distribution due cosmic variance with McLure data in the no-dust
 attenuation model.}
\label{fig:OD3_CosmicVar1_wo_dust}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}
\epsscale{1.00}
\plotone{fig/smallcells/OD4_plotcosmicvariance_w_dust.pdf}
\caption{Best fit parameter distribution due cosmic variance with Finkelstein data in the dust
 attenuation model.}
\label{fig:OD4_CosmicVar1_w_dust}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/smallcells/OD4_plotcosmicvariance_wo_dust.pdf}
\caption{Best fit parameter distribution due cosmic variance with McLure data in the no-dust
 attenuation model.}
\label{fig:OD3_CosmicVar1_wo_dust}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}
\epsscale{1.00}
\plotone{fig/SFR_DMHM_wo.pdf}
\caption{Star formation rate as function of the dark matter halo mass without dust attenuation. 
Solid lines represents our model's mean SFR value within $50\%$  shaded region. 
Comparison with the GALFORM semi-analitical model \citep{Gonzalez14} (dashed line within the 
$50\%$ shaded region) and a an implementation of abundance matching model \citep{Behroozi13}
(black circles). }
\label{fig:SFR_DMHM_wo}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/SFR_DMHM_w.pdf}
\caption{Star formation rate as function of the dark matter halo mass with dust attenuation. 
Solid lines represents our model's mean SFR value within $50\%$  shaded region. 
Comparison with the GALFORM semi-analitical model \citep{Gonzalez14} (dashed line within the 
$50\%$ shaded region) and a an implementation of abundance matching model \citep{Behroozi13}
(black circles). }
\label{fig:_SFR_DMHM_w}
\end{figure}
